D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-01 ootavacuous.tex
Add to Future Directions section
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

>>>>

This paper considers only fragments of programs whose threads
communicate using shared memory.
Future work might include the effects of input and output, as well
as code that reads out the current time, that uses thread IDs,
or that operates on pointer values.

Finally, future work might more precisely delineate the limits of
quasi-volatile behavior.
